### 2022-09-29 paper/200-base-language.tex
Work on writing

@@

\subsection{Beta Reductions}
//todo

>>>>

\subsection{Beta Reductions}
A unique requirement for dependently typed languages is beta reduction during typechecking, since types may require evaluation to compare.  In this section, we will define three rules, \verb|expectBetaEq|, which compares two expressions and checks if they're equal, \verb|betaReduce|, which fully evaluates an expression, and \verb|betaReduceHead|, which evaluates the head of an expression.

Starting with the latter, the signature of \verb|betaReduceHead| is the following, taking in an expression with a scope, and also returning and expression with a possibly different scope.

\begin{lstlisting}
betaReduceHead : (scope * Expr) -> (scope * Expr)
\end{lstlisting}

@@
